Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-06-11 summary.tex
0611

\begin{document}
\title{Efficient Non-incremental Constructive Solid Geometry Evaluation for Triangular Meshes}
\author{Rui~Wang,~
        Xudong~Jiang,~
        Hongbo~Fu,~
        Bin~Sheng,~and
        Enhua~Wu
\IEEEcompsocitemizethanks{

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

Main Contribution:

1. We develop a united representation of intersection lines between CSG primitives. Under this representation, Face re-tessellation and classification can be done robustly in any degenerate cases by our pipeline, while keeping good performance.

2. Unlike any of the previous method, during the algorithm, we conduct point-in-polyhedron tests only on single seed vertex. We develop a propagating to spread the classification information from the seed vertex into the whole CSG. In addition, because of this, we do not need to build a full space division to accelerate point-in-polyhedron tests, which is usually time-consuming.

@@

\section{Background}

\subsection{Plane-based geometry}

\subsection{CSG evaluation}

\section{Overview}
费大幅度发
\label{sec:overview}

\iffalse
\begin{figure*}[!t]
\centering
\includegraphics[width=7.1in]{flowchart}
\caption{}
\label{fig_overview}
\end{figure*}
\fi

Our method follows the paradigm of two-step Boolean operation---intersection detection and facet classification, together with an extra step of pre-computation to accelerate the intersection detection. The main feature of our method is that we design a unified representation of intersection between primitives (U-rep) to control the complexity of intersection detection result and simplify the facet classification. Also, plane-based representation is applied throughout the methods to ensure no error introduced. For the same reason, we compute indicator vectors of vertices rather than of the barycenter of facets during classification and deduce the facets' indicator vectors from its vertices'.

\subsection{Space division}

This step is the mainly the preparation for intersection detection. As intersection detection is performed between each pair of faces, localization is necessary for acceleration by filtering invalid pairs. In general, any space division data structure can be applied in this stage. For simplicity, our method uses the adaptive octree. The implementation is akin to the implementation in ?? et al.'s method \cite{feito2015fast}. Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}. Otherwise, it is a \emph{critical cell}. The big difference between our construction method and ??'s is the subdivision termination condition. In ??'s method,??. However, in our method, we do not need subdivide any non-critical cell no matter how many faces it contains. This is because subdividing non-critical cells benefits only the polyhedron inclusion test, which is frequently used in ??'s method but rarely in ours. This simplification can bring large performance advantage, especially for those cases whose intersection areas are small.

\subsection{Intersection detection}

The goal of this step isIntersection detection is performed between pairs of triangle faces within each critical cell. For the sake of robustness, all degenerated cases should be classified and well-handled.

\subsection{United representation of intersection}
\label{sec:overview:isect}

\subsection{Flood-Filling facet classification}

\section{Construction of United Intersection Graph }

The intersection of primitives can be very complex because of so many degenerate cases. In order to design a robust algorithm, one have to take into consideration of all the degenerated cases, which often makes the algorithm rather complex and error-prone to implement. We observe the important fact that the CSG evaluation is no more than splitting and selecting faces. Therefore, the only important thing during intersection test is to find out the potential edges and vertices of the result mesh. Therefore, we use a very concise graph model, with only a few extra data for classification on vertices, as the output of this stage.

Another problem is that numerical error introduced by computing coordinates of intersection vertices often leads to fault topology construction in the later stage. Using high precision float point is the most common way to alleviate this issue. However, only the time-consuming rational number arithmetic can be absolutely precise.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.5in]{p-reps}\\
  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies. }\label{fig_p-reps}
\end{figure}

 In order to be both robust and efficient, we choose not to compute the coordinates of intersection vertices until we finally construct the result topology. In the early stage, each new vertex is represented by intersection of three planes. This method is based on two facts: 1) Douze et al. [] observe that every intersected vertex is either the intersection between an edge and a plane, or the intersection of three planes. 2) Campen et al. [] give an efficient method to precisely convert b-reps mesh into its plane-based representation (Fig. \ref{fig_p-reps}). Details is explained in the following.

\subsection{Definition}

Faces in a certain primitive can be classified into intersected faces and non-intersected ones according to whether they intersect other primitives. Our United Intersection Graph (UI-graph) is a graph data structure embedded in each intersected face. It is used to split these faces and guide the face classification.

The nodes of UI-graph of an intersected face $F$ are the vertices, include the original three corners of $F$ and all the intersected vertices within $F$. Intersected vertices are shared between different UI-graphs. For example, the vertex $a$ is generated by intersection between face $F_1$ from primitive $P_i$ and edge $e(G_1, G_2)$ from primitive $P_j$, where $e(G_1, G_2)$  is the shared edge of face $G_1$ and face $G_2$. Then face $F_1$, $G_1$, $G_2$ are all intersected faces and each of them contains a UI-graph with one of its node is $a$.

Douze et al. [] observed that vertices during a CSG evaluation can be divided into three types. The first order vertex is already contained in the input primitives. The second order vertex is the intersection between an edge and a face. The third vertex results from intersection of three faces from different primitives. Considering the degenerate cases, this classification is not complete because different types do overlap. But it does not matter because each vertex at least belong to one of these types. Then we can use the plane-based representation (Fig. \ref{fig_p-reps}) introduced by Campen et al.[], which treats each triangle face by a supporting plane surrounded by three bounding planes, to represent each vertex by intersection of three planes. This method has two advantages. First, it is universal for all kinds of vertices, thus is easy to handle. Second, we can avoid explicitly computing the coordinates of new introduced vertices to avoid introducing numerical error.

Also, each node contains data structure called vertex context. It records on which primitives and on which part of primitive the node lies. A vertex can lies on the vertex, edge or within the face of a certain primitive. For example, the vertex context of $a$ is $\{(F_1, P_i), (e(G_1, G_2), P_j)\}$. This information is very important for the classification of the neighborhood. In particular, we notice that the vertex context of a certain vertex is invariant in different UI-graphs. So we only need to maintain one context for each vertex and shared among UI-graphs.

The edges of UI-graph are simply the intersection line segments between faces of different primitives. They are represented by two references of the nodes in the UI-graph. No further information is required.

As will explained below, we take two steps to construct UI-graphs for each intersected faces of the whole CSG. The first step is to build stand-alone UI-graphs for each pair of primitives, which is built upon our plane-based triangle-triangle intersection test, and the second step is to merge them into a single one for each intersected faces.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.7in]{raw3}\\
  \caption{The UI-graph of a certain face. }\label{fig_raw3}
\end{figure}

\subsection{Plane-Based Triangle-Triangle Intersection}

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{projection}
\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$. $Seg_2$ is the intersection between $S_1$ and $F_2$. The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
\label{fig_projection}
\end{figure}

The plane-based triangle-triangle intersection (PTTI) test is largely the variant of M\"{o}ller's triangle intersection test []. M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps, as illustrated in Fig. \ref{fig_projection}. First, an early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$. This is a necessary condition of intersection between $F_1$ and $F_2$. If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$. Second, the intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed . At last, the intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .

@@

Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and usual float point arithmetic. However, this is neither exact nor robust. In Fig. \ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation. Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation. Actually, the non-robustness of this algorithm is from \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones. In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig. \ref{fig_projection}) are computed as intermediate results. On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.

Fortunately, according to Sugihara and Iri \cite{sugihara1990solid}, geometry computation of Boolean operations can be restricted to predicates using plane-based representation of polyhedra. This motivated us to integrate plane-based representation into M\"{o}ller's algorithm. Exact and efficient predicate computation is performed using precise geometry predicate techniques \cite{shewchuk1997adaptive}. Details of our implementation are shown below.

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.7in]{p-reps}\\
  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
\end{figure}

>>>>

\begin{document}
\title{Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives}
\author{Rui~Wang,~
        Xudong~Jiang,~
        Hongbo~Fu,~
        Bin~Sheng,~and
        Enhua~Wu
\IEEEcompsocitemizethanks{

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical}: union, intersection and difference. CSG is often represented by a binary tree, called a CSG tree, whose leaves are primitives and whose internal nodes are Boolean operations.

CSG can be converted into the widely-used  boundary representation (i.e., triangle mesh) through boundary evaluation. It is an classical topic with history of over three decades. However, one always have to make a bargain between robustness and efficiency of the boundary evaluation. One could use rational number arithmetic to avoid errors and thus ensure unconditional robustness, which could be over 20 times slower than a non-robust one [?]. On the other hand, using an approximate method for boundary evaluation can be very fast, but lack exactness.

Most recent methods [???] try to find a faster way to evaluate boundary of CSG, yet for robustness, the answers are often ambiguous workarounds, like setting a tolerance [?], using higher precision float point number [?] or rotating the primitive with small angle to avoid coplanar cases [?], etc. These tricks are often too vague to implement, heavily depend on the experiments, thus not reliable. Campen et. al. [?] gave a good paradigm of a unconditional robust and exact boundary evaluation methods. It proved to be fairly efficient, and never crashed with legal inputs. Since then, few exact evaluation methods declare themselves as an unconditional robust one.

We prove that exact boundary evaluation of CSG can be even faster, while keeping unconditional robust. We adapt the plane-based techniques of Campen et. al.'s method for robustness, but use a framework very different from Campen et. al.'s, taking advantage of the recent popular idea of using geometry connectivity for face classification acceleration. In addition, unlike many other methods, our method can perform boundary evaluation directly for CSG with more than two primitives. That is, we do not incrementally generate the intermediate meshes of each Boolean operation. In opposite, we generate the final mesh directly. In this way, extra complexity of method is introduced, but we can save much computation time. The experiment shows that our method is much faster than Campen et. al.'s method, while only about twice slower than the state-of-art non-robust methods [??].

@@

\subsection{Plane-based geometry representation}

The primary information of commonly used representation of solids are the vertex coordinates. In this way, edges and faces are implicitly represented by combination of vertices. In contrast, in plane-based representation, the primary elements are planes. Vertices and edges are all implicitly represented by plane intersections.

The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Plane-based representation provides one important advantage
when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron – it is composed of a subset of the planes of the input polyhedra. Hence, opposed to the case of using vertex coordinates, that inevitably necessitates the construction of new geometry information, only geometric decision predicates are required to compose the output polyhedron from the face planes of the input. Since the input is usually given in a numerical representation with finite precision, we can determine an upper bound on the precision that is needed to make correct decisions. The a priori knowledge of this upper bound allows us to use fixed precision predicates that are specifically tailored to the precision required in the worst case, resulting in a vastly better performance compared to techniques for arbitrary numerical precision, that are usually required when
constructions are part of the processing. Our processing is rigorously based on this paradigm of plane-based geometry representation that allows us to perform fully robust, exact computations using only fast fixed precision predicates. These predicates take planes as arguments and check coincidence and co-orientation of planes, orientation of a plane with respect to a point defined by the intersection of three planes, and whether three planes intersect in a unique point. The latter one can also be used in negated form to check if three planes, that are known to intersect in a common point, even intersect in a common line. We implement them using filtering techniques proposed by Shewchuk.

\subsection{Exact evaluation methods}

CSG evaluation has had notorious problems with robustness since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. The non-robustness is inherited from the building blocks of CSG: Boolean operations on solids. Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces. For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.

\subsection{Approximative evaluation methods}

With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations. These methods often have good performance and are suitable for interactive applications, such as digital sculpting. However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.

\section{Motivation and Overview}

\label{sec:overview}
Our method is designed for boundary evaluation of Boolean operations on arbitrary number of primitives. Input primitives should be watertight and non-manifold  triangle meshes, represented by halfedge structures\cite{mcguire2000half}. Our method is unconditional robust, exact, while keeping good performance. In this section, we first introduce the motivation of our method, then describe where we start to design our boundary evaluation method. At last, we give the overview of the method.

\subsection{Motivation}
\label{sec:paradigm}

The boundary evaluation is in essence a process of selection. In other words, given a Boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh. Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified in a whole, since some of them intersect other primitives. Therefore, we need an extra step aiming at detecting the intersection between primitives and performing the tessellation. In general, most of the boundary evaluation methods follow the two-step paradigm  \cite{wang2011approximate} above, which consists of intersection computation and face classification.

During the intersection computation, primitive facets are tested in pairs to compute their intersection. Each input primitives are tessellated according to the intersection test results, making every face be either inside, outside or on the boundary of other primitives. They are what we called \emph{non-intersected meshes}. Every face of non-intersected meshes can be classified in a whole during classification. Unfortunately, under common float-point coordinate system, intersection test is error-prone. There are mainly two causes: first, there are a large amount of degenerate cases which are hard to be exactly detected; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates usually can not be exactly represented by float-point number.

Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $\Phi$ :
\begin{equation}
\lambda_\Phi(x) = \Phi(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
\end{equation}
The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$. This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\vec{\lambda}(x)$ for short). A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}). The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.

Face classification also suffers from robustness and exactness problems. Many methods classify face according to the indicators of its barycenter, and use point-in-polyhedron test to compute these indicators. However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification. In addition, to classify a single face, all the components of its space indicator vector must be figured out. Considering the large amount of faces, acceleration is usually necessary. Many algorithms take the benefits of the local coherence of indicators, classifying neighboring faces together. While this does improve the performance, it can make the exactness problem worse because the false classification can be propagated to neighboring faces.

We want to develop a new boundary evaluation method based on the two-step paradigm, keeping unconditional robust, exact and as fast as possible. Combined with the analysis above, we think our method should includes the following features:
\begin{itemize}
    \item It has to avoid errors when introducing new vertices during intersection computation. All degenerate cases of intersection have to be well resolved.
    \item Face classification has to be exact. On the other hand, acceleration using local coherence of indicators may be helpful.
    \item The exactness and robustness should not rely on arbitrary precision arithmetic, because it is too slow. Instead, we choose the plane-based techniques from \cite{bernstein2009fast}\cite{campen2010exact} to ensure good performance.
\end{itemize}

\subsection{Linked halfedge}

\label{sec:meshes}
We make an essential observation that the non-intersected meshes, as intermediate result of intersection computation, plays a very important role of the method design. It is a bridge that controls the complexity of intersection computation and facilitates the face classification. After the non-intersected meshes is determined, all things left are how to construct such a data structure and how to classify according to it.

Our non-intersected mesh, called linked halfedge, is a variance of halfedge, a well-known data structure to represent solids. Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to create simpler algorithm and better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.

However, naive halfedge is far from enough. The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points. Therefore, we utilize plane-based representation to avoid computing new coordinates. In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called linked halfedge). This information is used for avoiding repetitive vertices, reconstructing geometry connectivity, and ensuring the topology correctness.

Enlightened by Feito et. al. \cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing. Therefore, we add extra information into the linked halfedge, called \emph{intersection context}, to facilitate afterwards face classification. Intersection context identifies where an intersection lies on the surface of the related primitives. An edge of linked halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives. We will give the definition and usage of intersection context in details in the following sections.

To give a overall impression of how we design linked halfedge, we summarize the above content and highlight the following features:

\begin{itemize}
  \item Each input primitive mesh is tessellated into a linked halfedge. Faces in a linked halfedge must not cross any other linked halfedges.
  \item Coincident vertices between different linked halfedge should be linked, that is, coincident vertices are shared among linked halfedges.
  \item If a certain edge of linked halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
\end{itemize}

\subsection{Method overview}

\subsubsection{Space division}

This step is the preparation of intersection detection. As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand. In general, any space division data structure can be applied in this step. We use the adaptive octree for its simplicity. Our implementation is akin to the implementation in \cite{ogayar2015deferred}. Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}. Otherwise, it is a \emph{critical cell}.

The difference between our space division and many others \cite{ogayar2015deferred}\cite{feito2013fast} is the octree node subdivision termination criterion. In our method, we do not need subdivide any non-critical cell no matter how many faces it contains. This is because subdividing non-critical cells benefits only the ray-casting point-in-polyhedron test, which rarely appears in our method. This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions.

\subsubsection{Intersection detection}

This step is to detect intersections between primitives in a robust and exact way. Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles. However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues when computing the coordinates of new vertices. To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra \cite{sugihara1990solid} into the implementation of M\"{o}ller's algorithm. Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation. Moreover, to make our method robust, we classify all the intersection cases into three major classes and respectively discuss how to each condition. Details are provided in Section \ref{section:isect}.

\subsubsection{Tessellation}

Once all intersections are detected, we need to tessellate the input primitives and construct the linked halfedges.. In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT. However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during the previous step. Also, intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly. Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes. Therefore, we design a simple structure, called tessellation graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct linked halfedges from tessellation graphs, which is suitable for dealing with plane-based representation of intersections. Details are shown in section \ref{sec:tessellation}.

\subsubsection{Face classification}

This step is to choose faces from the linked halfedges to generate the final mesh. Literally compute all the space indicators of each face is unacceptable slow for large CSG trees. Enlightened by Feito et. al. \cite{feito2013fast}, we utilize the geometry connectivity to accelerate this process. In Feito et. al.'s method, the faces of tessellated meshes are first grouped according to whether they have the same indicator vector. After the grouping, each group is classified as a whole. This is based on the observation that indicators of faces are spatially coherent. That is, if a face $f$ is outside of primitive $M_0$, the neighbor of $f$ are likely to be out of $M_0$, too. Different from Feito et. al.'s method, we also consider the condition when the number of primitives is larger than two. In this condition, space vector of a face may be partly the same with its neighborhoods'. That is, we allow space indicators not only share within faces of the same group, but also among different groups and even primitives. This is useful when the number of primitives is large, or intersections between primitives is complex. Details will be shown in section \ref{sec:classification}.

\section{Plane-based geometry}

Vertex coordinates are commonly used in geometry computation. However, vertex coordinates suffer from inexact representation of intersection point between primitives. Therefore, we choose to use planes-based representation of polyhedrons and implicitly represent vertex by plane intersection. We start with a quick review of the basic conception of plane-based representation. After that, we introduce two substrates related to plane-based representation used in our method, since these two are rarely seen in related researches. Other substrates of plane-based representation can be seen in \cite{bernstein2009fast}.

\subsection{Conversion}

\label{sec:convert}

As we discussed in Section \ref{sec:paradigm}, one of the problem in Boolean evaluation under vertex-based representation is it inevitably introduces new vertices, whose coordinates cannot be exactly represented using standard float-point number. On the other hand, if plane-based representation is used, no new geometry information needs to be constructed---the result mesh is composed of the planes of the input primitives. Therefore, we can use only geometric decision predicates to perform the Boolean operation.

Using plane-based representation, each face of polyhedron is represented by a supporting plane $S$, where the face lies, and a list bounding planes $\{B_i\}$, each corresponding an edge of the face. Edge line is represented by intersection of $S$ and the related $B_i$. Corner point is then the intersection of $S$ and two consecutive bounding planes $B_i$ and $B_{i+1}$. Efficient and exact conversion from the vertex-based representation to plane-based representation is described in detail in \cite{campen2010exact}. If the input vertex coordinates precision is $L$, the maximum precision $P$ required to represent the plane coefficients is:
\begin{equation}
\label{eq:precision}
P = (L-1)+2(K-1)+3+1,
\end{equation}
where $K$  is the maximum bits to represent edge vector coordinates. If the plane coefficient has $M$ bit precision, $M$ have to greater than $P$ for exact representation. We rigorously enforce the criterion to $M \ge P+1$, and we will explain it in section \ref{sec:embed}.

Let $\delta = 2^{K-L-1}$ be the relative length (in max-norm) of the
longest edge in the mesh (relative to the bounding box). If we use IEEE 754 double precision ($M=53$) and assume $\delta \le 2^{-5.5}$, the maximum input precision $L$ can reach to 20, which is enough for most CAD application. As the precision of input coordinates is finite, we can determine in advance the upper boundary of precision needed to perform a precise decision, with which we can use fixed precision predicates techniques to gain much performance while keeping exactness. We implement the predicates using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.

\subsection{Substrates}
\label{sec:substrates}
Our method rigorously follows the paradigm of plane-based geometry. All decision predicates are computed using planes as input. These predicates include checking coincidence and co-orientation of planes, orientation of a plane with respect to a point, and whether three planes intersect in a unique point, etc. We omit the discussion of the predicates which is already in prior work \cite{bernstein2009fast,banerjee1996topologically}, and focus on specific predicates in our method in the following.

Before we start the discussion, we first introduce several regulations frequently used in the rest of our paper. A plane $P_x$ can be represented by plane coefficients $(a_x, b_x, c_x, d_x)$. The normal of $P_x$ is denoted as $\vec{N}_x$. Under plane-based representation, a line $L$ can be represented by intersection of two planes $(P_m, P_n)$, or in short $L: (P_m, P_n)$. The positive direction of $L$ is defined by cross product of the normals of $P_a$ and $P_b$, that is, $\vec{L}=(a_m, b_m, c_m) \times (a_n, b_n, c_n)$. A point $p$ is represented by plane triples $(P_a, P_b, P_c)$, or in short $p: (P_a, P_b, P_c)$.

Given two points $p$ and $q$ in the same edge line $L: (P_u, P_v)$, the two points can be represented by plane triples $(P_u, P_v, P_p)$ and $(P_u, P_v, P_q)$, sharing the same first two components. We want to determine if $q$ is in positive side of $p$ along the $\vec{L}$. We call this two-point comparison. This predicates can be converted to the problem of orientation of a plane $P_p$ with respect to a point $q$, except that there is an extra request---we have to guarantee cosine between $\vec{L}$ and the normal $\vec{N}_p$ be positive, that is:
\begin{equation}
\label{eq:pointcomp}
   \left|
  \begin{array}{ccc}   %该矩阵一共3列，每一列都居中放置
  a_u  & b_u & c_u \\
  a_v  & b_v & c_v \\
  a_p  & b_p & c_p
  \end{array}
  \right| > 0,
\end{equation}
If not, we negate $P_p$ to be the test plane. The computation of this predicates is described in \cite{bernstein2009fast}.

Another predicates is used when tessellating a face (further explanation of its application is shown in Section \ref{}). Given two lines $L_a: (P_s, P_a)$ and $L_b: (P_s, P_b)$, which are on the same plane $P_s$, we want decide whether the sign of cross product of $\vec{L}_a$ and $\vec{L}_b$ has the same orientation as the normal $\vec{N}_s$. Direct solution requires to explicitly compute the vector of $L_a$ and $L_b$ and then decide the sign by $\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)$. However, explicit representation of $\vec{L}_a$ and $\vec{L}_b$ requires more bits than standard double precision float point number, bringing extra computation burden.

To solve this, we decompose the normal vectors of $P_a$ and $P_b$: $\vec{N}_a = \vec{N}^\parallel_a + \vec{N}^\perp_a$ and $\vec{N}_b = \vec{N}^\parallel_b + \vec{N}^\perp_b$. Here superscript `$\parallel$` means the vector is in the plane $P_s$ and `$\perp$` means it is orthogonal to $P_s$. Then $\vec{N}_a \times \vec{N}_b = \vec{N}^\parallel_a \times \vec{N}^\parallel_b + \vec{N}^\perp_a \times \vec{N}^\parallel_b + \vec{N}^\parallel_a \times \vec{N}^\perp_b + \vec{N}^\perp_a \times \vec{N}^\perp_b$. As we know $\vec{N}^\perp_a$ and $\vec{N}^\perp_b$ is parallel, $\vec{N}^\perp_a \times \vec{N}^\perp_b = \textbf{0}$. Now, we evaluate the expression: $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)$. Since $\vec{N}_s$ is orthogonal to both $\vec{N}^\perp_a \times \vec{N}^\parallel_b $ and $\vec{N}^\parallel_a \times \vec{N}^\perp_b $, we deduce $\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b) = \vec{N}_s \cdot (\vec{N}^\parallel_a \times \vec{N}^\parallel_b)$. Here we make an essential observation that $\vec{N}^\parallel_a \times \vec{N}^\parallel_b$ has the same direction as $\vec{L}_a \times \vec{L}_b$, that is:
\begin{equation}
\label{eq:cosine}
sign(\vec{N}_s \cdot (\vec{N}_a \times \vec{N}_b)) = sign(\vec{N}_s \cdot (\vec{L}_a \times \vec{L}_b)),
\end{equation}
which means we do not need to explicitly compute $\vec{L}_a$ or $\vec{L}_b$. Instead, we only have to evaluate the left expression of equation \ref{eq:cosine}.

\section{Exact Intersection Detection}

\label{section:isect}
In this step, intersections between faces are computed through the triangle-triangle intersection test within each critical cell. We adopt M\"{o}ller's intersection detection algorithm \cite{moller1997fast} on account of its efficiency and simplicity. However, because collision detection algorithms are often accompanied by non-robustness problems, a conventional implementation of this algorithm may cause unpredictable results. Therefore, we integrate plane-based geometry representation \cite{sugihara1990solid} into M\"{o}ller's algorithm to make it unconditionally precise and robust. In the following, we first make a quick review of M\"{o}ller's algorithm, then discuss the way to make it unconditional robust. At last, we talk about how to deal with degenerate cases.

\subsection{Vertex-based method review}

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{projection}
\caption{$Seg_1$ is the intersection between $S_2$ and $F_1$. $Seg_2$ is the intersection between $S_1$ and $F_2$. The intersection between $F_1$ and $F_2$, which is the line segment in red, is the overlap of $Seg_1$ and $Seg_2$.}
\label{fig_projection}
\end{figure}

M\"{o}ller's algorithm computes the intersection between two triangles $F_1$ and $F_2$ in three steps (Fig. \ref{fig_projection}).
\begin{itemize}[leftmargin=0.45cm]
\item[1)] An early rejection is performed by testing whether $F_1$ intersects the plane where $F_2$ lies, which is denoted as $S_2$. This is a necessary condition of intersection between $F_1$ and $F_2$. If this test is passed, then the same is performed for $F_2$ and $S_1$, where $S_1$ is the plane of $F_1$.
\item[2)]The intersection between $F_1$ and $S_2$, denoted as $Seg_1$, and the intersection between $F_2$ and $S_1$, denoted as $Seg_2$, are separately computed .
 \item[3)]The intersection between $F_1$ and $F_2$ is determined by computing the overlap area of $Seg_1$ and $Seg_2$ .
\end{itemize}

@@

Conventional implementations of M\"{o}ller's algorithm use vertex-based representation and common float point arithmetic, which is neither exact nor robust. In Fig. \ref{fig:precision}, we illustrate a non-robust 2D case of the Boolean operation. Although implementing M\"{o}ller's algorithm with arbitrary precision arithmetic could make it robust, it is too costly for a large CSG evaluation. Actually, the non-robustness of this algorithm is from geometry \emph{constructions} \cite{bernstein2009fast}, which compute new coordinates of geometry objects based on the known coordinates of existing ones. In M\"{o}ller's algorithm, the coordinates of $Seg_1$ and $Seg_2$ (Fig. \ref{fig_projection}) are computed as intermediate results. On the other hand, if the computation can be restricted to \emph{predicates}, which make a two or three-way decision based on known coordinates, we could quickly and robustly implement this algorithm.

\subsection{Plane-based technique embedding}

\label{sec:embed}
According to the method described in section \ref{sec:convert}, triangle faces $f$ are firstly converted to its plane-based representation: a supporting plane $P_{s,f}$ surrounded by three bounding planes $P^i_{b,f}, i = 1,2,3$. We introduce the plane-based implementation of M\"{o}ller's algorithm step by step in the following:

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{sign}
\caption{We denote the signed distance from point $X$ to plane $S_2$ as $d_X$. All the four conditions of intersection between $F_1$ and $S_2$ (denoted as $Seg_1$) are:  (a) $d_A\cdot d_C<0$, $d_B\cdot d_C<0$; (b) $d_A=0$, $d_B=0$, $d_C\neq 0$; (c) $d_A=0$, $d_B\cdot d_C<0$; (d) $d_A=0$, $d_B\cdot d_C>0$. End points of $Seg_1$ are intersections between $S_2$ and related edge lines of $F_1$ (bold edges).}
\label{fig:isect}
\end{figure}
